Appendix S2: Data Exploration

### 2023-04-20 ms/shida-no-kai-figs.Rmd
Add PE plot

ggsave("working/shida-no-kai/richness.png")
```

>>>>

ggsave("working/shida-no-kai/richness.png")

# Fern PE
# - map
a <-
  ggplot() +
  geom_sf(data = japan, fill = "grey90", color = "black", lwd = 0.25) +
  geom_sf(data = biodiv_ferns_spatial, aes(fill = pe_obs_p_upper), color = "transparent", alpha = 0.8) +
  geom_sf() +
  scale_fill_scico(palette = "lajolla") +
  labs(fill = "PE P-value") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1), limits = c(ja_lat_min, ja_lat_max)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme() +
  theme(
    legend.title = element_text(size = 30/.pt),
    legend.text = element_text(size = 24/.pt),
    legend.justification=c(0,1), legend.position=c(0,1)
  )
# - latitudinal trends
b <- ggplot(ses_div_centroids, aes(x = latitude, y = pe_obs_p_upper)) +
  geom_point(color = "grey50", shape = 1 ) +
  geom_smooth(se = FALSE) +
  xlim(ja_lat_min, ja_lat_max) +
  coord_flip() +
  labs(y = "PE P-value") +
  trend_line_theme()
a + b + plot_layout(widths = c(3,1), heights = c(1,1))

ggsave("working/shida-no-kai/pe.png")

```
